Racial and Ethnic Differences in ETI

### 2024-04-03 Kamyron Jordan/Racial and Ethnic Differences in ETI/racial_and_ethnic_differences_in_eti.qmd
Update racial_and_ethnic_differences_in_eti.qmd

@@

```{r}
#| warning: false
# Plot
names(fit$strata) <- gsub("race=", "", names(fit$strata))
p <- fit %>%
  ggsurvfit(type = "risk") +
  xlim(c(0, 365 * 2)) +
  add_confidence_interval() +
  add_quantile() +
  ylab("Proportion on ETI") + xlab("Days From Eligibility") +
  theme_bw(base_size = 16) +
  theme(legend.title = element_blank(), legend.text = element_text(size = 14))
p
```

@@

```{r}
surv_dat$Insurance <- factor(surv_dat$Insurance,
  levels = c(
    "Health Insurance Policy (e.g. Private Insurance)",
    "Indian Health Service",
    "Medicaid",
    "Medicare",
    "More than one",
    "No Insurance",
    "Other",
    "State special needs program, e.g., BCMH, CCS, CRS, GHPP, etc.",
    "TriCare or other military health plan"
  ),
  labels = c(
    "Private", "Public", "Public", "Public", "More Than One", "No Insurance",
    "No Insurance", "Public", "Tricare"
  )
)
# FEV1 to categorical
surv_dat$fev1_cat <- cut(surv_dat$gli_fev1_ppred_rn,
  breaks = c(0, 40, 80, 100, Inf),right = F
)
label(surv_dat$fev1_cat)=label(surv_dat$gli_fev1_ppred_rn)
# New fit
new_surv_f <- update(surv_f, . ~ . + Insurance)
cox_res <- coxph(new_surv_f, data = surv_dat, cluster = eDWID)
cox_res %>%
  tbl_regression(exponentiate = T)
ggcoef_model(cox_res,
  show_p_values = F, add_reference_rows = F,
  signif_stars = F, colour = F, exponentiate = T
)
```

@@

```{r}
surv_dat$`Age Group` <- cut(surv_dat$encounterage,
  breaks = c(6, 12, 18, 30, Inf), right = F
)
new_surv_f <- update(surv_f, . ~ . + Insurance + `Age Group` +
  gli_fev1_ppred_rn)
cox_res <- coxph(new_surv_f, data = surv_dat, cluster = eDWID)
cox_res %>%
  tbl_regression(exponentiate = T)
ggcoef_model(cox_res,
  show_p_values = F, add_reference_rows = F,
  signif_stars = F, colour = F, exponentiate = T
)
```

@@

```{r}
encounter %>%
  group_by(eDWID, race) %>%
  summarise(
    `Visits per Year` = n() / length(unique(reviewyear)),
    .groups = "drop"
  ) %>%
  select(-eDWID) %>%
  tbl_summary(by = race)
```

>>>>

### 2020 - 2022

The table below includes everyone who was in the registry in 2020, 2021, or 2022. 
People were considered eligible for ETI if they were eligible any of the three years, and were considered prescribed ETI if they had Vx445comb="Yes" for any year. So, a person who was eligible in 2020 but not prescribed until 2022 would count the same as someone who was eligible in 2020 and started immediately.

```{r}
annual %>%
  filter(ReviewYear %in% 2020:2022) %>%
  group_by(eDWID) %>%
  summarise(race = race[1],eti_elig = any(eti_elig == "Yes"),
            on_eti = any(Vx445comb=="Yes")) %>%
  select(-eDWID) %>%
  tbl_summary(by=race) %>%
  add_overall() %>%
  add_ci()
```

@@

```{r}
#| warning: false
# Plot
names(fit$strata) <- gsub("race=", "", names(fit$strata))
p <- fit %>%
  ggsurvfit(type = "risk") +
  xlim(c(0, 365 * 2)) +
  add_confidence_interval() +
  add_quantile() +
  ylab("Proportion on ETI") + xlab("Days From Eligibility") +
  theme_bw(base_size = 16) +
  theme(legend.title = element_blank(), legend.text = element_text(size = 14),
        legend.position = c(0.7, 0.3))
p
```

@@

```{r}
surv_dat$Insurance <- factor(surv_dat$Insurance,
  levels = c(
    "Health Insurance Policy (e.g. Private Insurance)",
    "Indian Health Service",
    "Medicaid",
    "Medicare",
    "More than one",
    "No Insurance",
    "Other",
    "State special needs program, e.g., BCMH, CCS, CRS, GHPP, etc.",
    "TriCare or other military health plan"
  ),
  labels = c(
    "Private", "Public", "Public", "Public", "More Than One", "No Insurance",
    "No Insurance", "Public", "Tricare"
  )
)
# FEV1 to categorical
surv_dat$fev1_cat <- cut(surv_dat$gli_fev1_ppred_rn,
  breaks = c(0, 40, 80, 100, Inf), right = F
)
label(surv_dat$fev1_cat) <- label(surv_dat$gli_fev1_ppred_rn)
# New fit
new_surv_f <- update(surv_f, . ~ . + Insurance)
cox_res <- coxph(new_surv_f, data = surv_dat, cluster = eDWID)
cox_res %>%
  tbl_regression(exponentiate = T)
ggcoef_model(cox_res,
  show_p_values = F, add_reference_rows = F,
  signif_stars = F, colour = F, exponentiate = T
)
```

@@

```{r}
surv_dat$`Age Group` <- cut(surv_dat$encounterage,
  breaks = c(6, 12, 18, 30, Inf), right = F
)
new_surv_f <- update(surv_f, . ~ . + Insurance + `Age Group` +
  fev1_cat)
cox_res <- coxph(new_surv_f, data = surv_dat, cluster = eDWID)
cox_res %>%
  tbl_regression(exponentiate = T)
ggcoef_model(cox_res,
  show_p_values = F, add_reference_rows = T,
  signif_stars = F, colour = F, exponentiate = T
) 
```

@@

```{r}
encounter %>%
  group_by(eDWID, race) %>%
  summarise(
    `Visits per Year` = n() / length(unique(reviewyear)),
    .groups = "drop"
  ) %>%
  select(-eDWID) %>%
  tbl_summary(by = race) %>%
  add_p()
```
